---
title: "Part 1: Demographics"
output: html_notebook
---

```{r, echo=FALSE}
library(tidyverse)
fulldata <- fulldata %>%
  mutate(Age = as.numeric(Age))
```

The sample was slightly skewed female, with `r round(length(which(fulldata$Gender=="Female"))/length(fulldata$Gender)*100,1)`% of the sample (n = `r length(which(fulldata$Gender=="Female"))`) female.

Ages of participants in the sample ranged from `r min(fulldata$Age, na.rm=T)` to `r max(fulldata$Age, na.rm=T)`. The average age was `r round(mean(fulldata$Age, na.rm=T),1)`, and the median was `r round(median(fulldata$Age, na.rm=T))`. The histogram below shows the breakdown of age.

```{r}
fulldata %>%
  ggplot(aes(Age)) +
  geom_histogram(binwidth = .8)
```

##Reigon

Regionally, the sample was diverse, drawn from a number of areas across the UK. 

```{r}

```

##Class and income

The UK has something called a social grade which is used to classify social class. 

```{r}
fulldata %>%
  filter(!is.na(`Social Grade`)) %>%
  filter(`Social Grade`!="(Refused)") %>%
  count(`Social Grade`) %>%
  ggplot(aes(reorder(`Social Grade`, n), n)) +
  geom_bar(stat='identity') +
  coord_flip()
```

Data was also collected on the average household income of the individiual, as shown in the graph below.

```{r}
fulldata %>%
  filter(Annual_household_income!="WEEKLY INCOME FIGURE") %>%
  ggplot(aes(Annual_household_income)) +
  geom_bar(stat='count') +
  coord_flip()
```

```{r}
typical_frequency %>%
  filter(Source==" The Daily Mail") %>%
  count(Source)
  left_join(select(fulldata, ID, `I am satisfied with my life`), by = "ID") %>%
  ggplot(aes(Frequency, `I am satisfied with my life`)) +
  geom_bar(stat='summary',fun.y = 'mean') +
  coord_flip()
```


